\chapter{Introduction}\label{chap_intro}

The World Bank Group lends billions of dollars each year to fund development projects in its efforts to reduce global poverty. This project helps investigators at the Bank search for patterns of collusion, corruption, and fraud in its contracts data, using models of contract-specific risk. By developing an automated approach to detect these offenses this project can help the World Bank efficiently target future investigations.


\section{The World Bank}

The World Bank was created in 1944 as one institution and has evolved into an association of five development institutions. It is composed by  the International Bank for Reconstruction and Development (IBRD), the International Development Association, the International Finance Corporation (IFC), the Multilateral Guarantee Agency (MIGA), and the International Centre for the Settlement of Investment Disputes (ICSID). In its interior it was formed by a large group of engineers and financial analysts who work from Washington, D.C. Now, they have a very heterogenous and distict staff that includes economist, public policy experts, sector experts and social scientists and  about one third of the workers has spread to the country officies 

% \parencite[The World ][]{wbhistory} 
\parencite{wbhistory} 
\cite{Bivand}

Reconstruction remains an important part of our work. However, at today's World Bank, poverty reduction through an inclusive and sustainable globalization remains the overarching goal of our work.

% The World Bank Group has set two goals for the world to achieve by 2030:
% 
% End extreme poverty by decreasing the percentage of people living on less than $1.90 a day to no more than 3\%
% Promote shared prosperity by fostering the income growth of the bottom 40\% for every country
% The World Bank is a vital source of financial and technical assistance to developing countries around the world. We are not a bank in the ordinary sense but a unique partnership to reduce poverty and support development. The World Bank Group comprises five institutions managed by their member countries.
% 
% Established in 1944, the World Bank Group is headquartered in Washington, D.C. We have more than 10,000 employees in more than 120 offices worldwide.
% 
% Financial Products and Services
% 
% We provide low-interest loans, zero to low-interest credits, and grants to developing countries. These support a wide array of investments in such areas as education, health, public administration, infrastructure, financial and private sector development, agriculture, and environmental and natural resource management. Some of our projects are cofinanced with governments, other multilateral institutions, commercial banks, export credit agencies, and private sector investors.
% 
% We also provide or facilitate financing through trust fund partnerships with bilateral and multilateral donors. Many partnershave asked the Bank to help manage initiatives that address needs across a wide range of sectors and developing regions.
% 
% Innovative Knowledge Sharing
% 
% We offer support to developing countries through policy advice, research and analysis, and technical assistance. Our analytical work often underpins World Bank financing and helps inform developing countries’ own investments. In addition, we support capacity development in the countries we serve. We also sponsor, host, or participate in many conferences and forums on issues of development, often in collaboration with partners.
% 
% To ensure that countries can access the best global expertise and help generate cutting-edge knowledge, the Bank is constantly seeking to improve the way it shares its knowledge and engages with clients and the public at large. Key priorities include:
% 
% Results: We continue to sharpen our focus on helping developing countries deliver measurable results.
% Reform: We are working to improve every aspect of our work: how projects are designed, how information is made available (Access to Information), and how to bring our operations closer to client governments and communities.
% Open Development: We offer a growing range of free, easy-to-access tools, research and knowledge to help people address the world's development challenges. For example, the Open Data website offers free access to comprehensive, downloadable indicators about development in countries around the globe. We have also madeWorld Bank Live—live discussions open to participants worldwide—a key part of our Spring and Annual Meetings with the International Monetary Fund.



Contractors providing goods and services on World Bank projects are typically hired through a competitive bidding process. Occasionally, prospective contractors influence the competitive system by colluding with other contractors, bribing government officials, or otherwise manipulating the bidding process. These offenses have far-reaching effects on the price and quality of contract delivery. The World Bank is committed to detecting instances of collusion, corruption, and fraud in order to maximize its global impact.