\chapter{Conclusion}\label{chap_conclusion}

From this project it is clear that identifying potential cases of corruption, collusion  and fraud is a difficult task. The good part is that there is a lot of space for improvement in the investigation process that the Integrity Vice Presidency performs. By now, they rely on whistle-blowers and third parties to fill complicated forms in their web  and mobile applications or to place calls to the World Bank so that they are able to start an investigation process that could be just based on competitors that are trying to slow the procurement process. Fortunately for them this project represents a viable way for them to perform investigations in a proactive way instead of having to wait for third parties to give them actionable arguments to investigate an entity or a project. Not only that, they can make their decisions based on objective data that might also help to prioritize their investigations so that they target the ones that have more impact.

This project showed that current data collected by World Bank on contracts is sufficient to forecast risk on future contracts, and as explained, these risk forecasts can allow World Bank investigators to be more proactive in determining which companies, projects and contracts to examine. This project suggest that future data collection should be done in a more standardized way such that they do not need to rely on an algorithm such as the Google searches algorithm  so that they are able to identify entities among different data sources within their own data. This might lead to changes in the way they start the procurements process, but this work is a clear example of the impact that a small change in the way they collect data from entities all over the world can make a huge difference. After modifying the way they collect data, future analysis could be able to identify separate risk levels for fraud, collusion and corruption.

Finally, this project serves as an example of how a real life problem should be approached as a data science problem, it demonstrates the importance of the relation between the partner and the data scientists and illustrates all the necessary elements a project like this should have.